\begin{appendices}
  \section{Collaboration Demographical Information}
  \begin{table}[h!]
    \centering  
    \begin{tabular}  {ccccccc}
  	  \hline
	  \hline
      \textbf{Name} &  \textbf{Role} & \textbf{Student Status} & \textbf{Race} & \textbf{Ethnicity} & \textbf{Gender} & \textbf{Disabled}\\
 	  \hline
 	  Andrew L. Renshaw & Faculty Mentor & Faculty & White & Non-Hispanic & Male & No\\ \hline
 	  Reed Masek & Project Leader & Undergraduate & White & Non-Hispanic & Male & No\\ \hline
 	  Jimish Patel & Astrobiology Coordinator & Undergraduate & Asian & Non-Hispanic & Male & No \\ \hline
      Taylor Hill & Radiation Coordinator & Graduate Student & White & Non-Hispanic & Male & No\\ \hline
      Daniel Howard & Electronics Coordinator & Undergraduate & White & Non-Hispanic & Male & No \\ \hline
      Jose Alvarado & Organic Solar Cells & Undergraduate & White & Hispanic & Male & No \\ \hline
      Carlos Amaya & Programming and Data Handling & Undergraduate & White & Hispanic & Male & No \\ \hline
      Aaron Boggs & Organic Solar Cells & Undergraduate & White & Non-Hispanic & Male & No \\ \hline
      Carson Bush & Astrobiology Planning and Construction & Undergraduate & White & Non-Hispanic & Female & No \\ \hline
      Alejandro Carpy & Organic Solar Cells & Undergraduate & White & Hispanic & Male & No \\ \hline
      Kevin Fleming & Astrobiology Construction & Undergraduate & White & Non-Hispanic & Male & No \\ \hline
      Sydney Giang & Mechanical Engineering and Construction & Undergraduate & Asian & Non-Hispanic & Female & No \\ \hline
      Emily Humble & Programming and Mechanical Control & Undergraduate & White & Non-Hispanic & Female & No \\ \hline
      Khoa Ngo & Astrobiology Construction & Undergraduate & Asian & Non-Hispanic & Male & No \\ \hline
      Huy Truong & Mechanical Engineering and Construction & Undergraduate & Asian & Non-Hispanic & Male & No \\ \hline
      Abraham Vega & Mechanical Design & Undergraduate & White & Hispanic & Male & No \\ \hline
	  Stuart George & MiniPIX Expert & Post-Graduate & White & Non-Hispanic & Male & No \\ \hline
	  Donna Pattison & Faculty Mentor, Microbiology & Faculty & White & Non-Hispanic & Female & No \\ \hline
	  Preethi Gunaratne & Faculty Advisor & Faculty & Asian & Non-Hispanic & Female & No \\ \hline
	\end{tabular}
  \end{table}

  \section{Outreach and Publications}
  \noindent As requested by the HASP administration, this section details the relevant outreach and publications by those who are or have been in the University of Houston HASP team.

  \noindent Some presentations do not have associated hyperlinks since the presentation was relatively informal and not for an official conference. 

  \vspace{0.25cm}
  \noindent\underline{Outreach and Presentations:}
  \begin{enumerate}[leftmargin=3\parindent]
    \item Steven Oliver, UH Undergraduate Research Day, October 12, 2017, URL no longer available.
  \item Samuel Morales, Bulletin of the American Physical Society, October 20, 2017, \url{https://meetings.aps.org/Meeting/TSF17/Session/E5.3}.
  %\item Fre'Etta Brooks
  \item Fre'Etta Brooks, Rice University, APS Conferences for Undergraduate Women in Physics (CUiP), January 14, 2017, \url{http://cuwip.rice.edu/cuwip_poster_session.html#poster15}.
  \item Steven Oliver, Andrew Walker, Kevin Portillo, and Reed Masek, Tarleton APS Conference Poster Presentation \url{http://meetings.aps.org/Meeting/TSS18/Session/D1.5}.
  \item Steven Oliver, Presentation at University of Houston STEM Center's STEM Saturday, October 13, 2018.
  \item Taylor Hill, Presentation at Mars Rover Celebration Award Ceremony, March 23, 2019.
  \item Reed Masek, Presentation for NASA's Aerospace Scholars, July 8, 2019.
  \end{enumerate}

  \noindent As of writing this report, there has been one publication conceived as a result of the HASP missions.
  The publication is in the end stages of writing, and will soon be sent to be reviewed by the publisher.
  The bibliography entry is as follows:

  \noindent (In Progess) S.A. Garcia Morelos, A. Walker, R. B. Masek, S. Oliver, F. Brooks, K.D. Portillo, J. Patel, D. Pattison, A. L. Renshaw \textit{MiniPIX Cosmic Ray Tracking and Radiation Dosimetry During SORA Stratospheric Balloon Flights}.
  
  \section{Internships, Jobs, Recent Graduates, and Graduate School}
  \noindent This section lists the internships and jobs received by participants in the UH HASP team.
  
  \vspace{0.5cm}
  
  \noindent The following is all of the HASP members who have received internships, the company or institution, the location, and the year of the internship.
  
  \vspace{0.25cm}
  \noindent\underline{Internships:}
  \begin{enumerate}[leftmargin=3\parindent]
  \item Kevin Portillo, Boeing Internship, Houston, Texas, 2018
  \item Reed Masek, DAAD RISE Internship, Karlsruhe, Germany, 2018
  \item Steven Oliver, NASA Johnson Space Center, Houston, Texas, 2019
  \end{enumerate}

  \vspace{0.5cm}
  
  \noindent The following is all of the HASP members who are working in industry, their company, their position, and the year they began.

  \vspace{0.25cm}
  \noindent\underline{Jobs:}
  \begin{enumerate}[leftmargin=3\parindent]
  \item Andrew Walker, NOV, Software Engineer, 2018
  \item Andrew Walker, Gene by Gene, Software Engineer, 2019
  \item Kevin Portillo, Chevron, Software Engineer, 2019
  \end{enumerate}

  \vspace{0.5cm}
  
  \noindent The following is all of the HASP members who have graduated within the past year, their degree, and when they graduated.

  \vspace{0.25cm}
  \noindent\underline{Recent Graduates:}
  \begin{enumerate}[leftmargin=3\parindent]
  \item Kevin Portillo, B.S. Computer Science, December 2018.
  \item Taylor Hill, B.S. Physics, May 2019.
  \item Jimish Patel, B.S. Physics, December 2019.
  \item Daniel Howard, B.S. Electrical Engineering, December 2019.
  \end{enumerate}

  \vspace{0.5cm}
  
  \noindent The following is all of the HASP members who are enrolled in graduate studies, the institution, program, and the year they began.
  
  \vspace{0.25cm}
  \noindent\underline{Graduate School:}
  \begin{enumerate}[leftmargin=3\parindent]
  \item Steven Oliver, Rice University, Space Studies Masters Program, 2017
  \item Fre'Etta Brooks, MD Anderson UT Health, Medical Physics Ph.D. Program, 2019
  \item Taylor Hill, Colorado State University, Masters in Materials Sciences Engineering, 2019
  \end{enumerate}

  \noindent The following are messages from previous HASP participants making personal comments on their successes after HASP and the experiences they had as part of the HASP program:

  \textit{``This month (December 2019) I will be graduating from Rice University with a Professions Science Master's Degree in Space Studies with a focus in engineering. I'm currently interning with Airbus Defence and Space (Space Systems, Inc.) as a Mechanical Design Engineer. I'm working on the design of the ArgUS multi-payload adapter mechanism for Bartolomeo external platform on the ISS. \newline
    I also received a summer 2019 internship with the Space Radiation Analysis Group (SRAG) at NASA JSC as a research intern. My project focused on the validation of an existing Monte Carlo tool for the simulation of a Timepix (cosmic radiation detector) data to various ion beam measurements. \newline
    I would like to thank the HASP program for allowing me to participate in the HASP 2017 and 2018 flights. My career path, education, and accomplishments prior mentioned directly stem from the experiences and skills I have gained from participating in the HASP flight program.''}
  \newline\hspace*{12cm} -Steven Oliver

  \vspace{2cm}

  \textit{``Soon after graduating from the University of Houston with a B.S Computer Science degree, I began working as a Software Engineer at Chevron in Houston. Specifically, I work within embedded IT for Chevron’s Pipeline and Power’s Business Unit where we operate and manage the transportation of product from Upstream to Downstream as well as the cogeneration and renewable energy assets for all of Chevron. My role involves developing, supporting, and migrating applications used by my business unit. Our partnership with Microsoft allows me to develop, build, and deploy modern applications all through the cloud.''}
  \newline\hspace*{12cm} -Kevin Portillo

  
\end{appendices}
